Federated Imputation

### 2020-07-16 synthesizing_partitioned_data.Rmd
Full boys data added

@@

>>>>

```{r, echo = F, dpi = 300}
boys_cart_results_10 %>%
  filter(Variable == "(Intercept)") %>%
  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
  geom_density(alpha = .4) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  ggtitle("Intercept") +
  theme_classic() -> plot_intercept

boys_cart_results_10 %>%
  filter(Variable == "age") %>%
  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
  geom_density(alpha = .4) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  ggtitle("Age") +
  theme_classic() -> plot_age

boys_cart_results_10 %>%
  filter(Variable == "hgt") %>%
  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
  geom_density(alpha = .4) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  ggtitle("Height") +
  theme_classic() -> plot_height

cowplot::plot_grid(cowplot::plot_grid(plot_intercept + theme(legend.position = "none"), 
                                     plot_age + theme(legend.position = "none"), 
                                     plot_height + theme(legend.position = "none"), 
                                     nrow = 1, align = 'vh'),
                  cowplot::get_legend(plot_age + theme(legend.position = "bottom")),
                                      ncol = 1, rel_heights = c(1, .1))
```

@@

```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
source("2.h Synthesize bootstrapped boys7482 data.R")
```

When we additionally do this with the `boys7482` data from the package `AGD`, we get slightly beter results. However, there remains a problem with regard to the bootstrapped samples from the population. So apparently, the bootstrapping procedure induces more variance than would be expected based on the $95\%$ CI. I am not sure why this error is introduced. Additionally, the synthesizing method seems to be somewhat biased, which can be seen in the density plots displayed after the tables.

```{r, echo = F}
knitr::kable(summary_cart_10_7482, digits = 3)
```

```{r, echo = F, dpi = 300}
boys_cart_results_10_7482 %>%
  filter(Variable == "(Intercept)") %>%
  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
  geom_density(alpha = .4) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  ggtitle("Intercept") +
  theme_classic() -> plot_intercept_7482

boys_cart_results_10_7482 %>%
  filter(Variable == "age") %>%
  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
  geom_density(alpha = .4) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  ggtitle("Age") +
  theme_classic() -> plot_age_7482

boys_cart_results_10_7482 %>%
  filter(Variable == "hgt") %>%
  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
  geom_density(alpha = .4) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  ggtitle("Height") +
  theme_classic() -> plot_height_7482

cowplot::plot_grid(cowplot::plot_grid(plot_intercept_7482 + theme(legend.position = "none"), 
                                     plot_age_7482 + theme(legend.position = "none"), 
                                     plot_height_7482 + theme(legend.position = "none"), 
                                     nrow = 1, align = 'vh'),
                  cowplot::get_legend(plot_age_7482 + theme(legend.position = "bottom")),
                                      ncol = 1, rel_heights = c(1, .1))
```
